Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
added screenshots
moved section down
added future work
added review management section

 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer. Section \ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.

@@

\section{Preliminary user study}
\section{Sketches}
\section{Conclusion}

>>>>

 %TODO fix section reference
 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer. Section~\ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.4]{snippetSelections.png}
\caption{Adding code snippets from various resources}
\label{fig:snippetSelection}
\end{figure}

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.45]{snippetViewer.png}
\caption{Viewing code snippets}
\label{fig:snippetViewer}
\end{figure}

@@

In time, the programmer creates many reviews as she seeks to improve herself and her code. She may also wish to keep certain reviews for future reference.

\croder keeps track of current and past reviews. Moreover, for each review it fetches the associated replies. Figure~\ref{fig:reviewBrowser} illustrates the Review Browser. The left pane shows the review titles while the right pane shows the replies for the currently selected review.

%TODO fix section reference
Section~\ref{sec:future} illustrates several features which can enhance the tool's capabilities via review management.

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.3]{reviewBrowser.png}
\caption{Viewing code snippets}
\label{fig:snippetViewer}
\end{figure}

\section{Preliminary user study}
\section{Sketches}

\section{Future Work}
\label{sec:future}

%expand bullets from presentation slides
%snippet selector
%review browser: respond, migrate to other browsers

\section{Conclusion}
